\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}

### 2021-07-15 Drafts and notes/Draft_06.tex
Almost final

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
\begin{equation}\label{heur1}
    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$. After taking derivative, heuristically, \eqref{heur1} becomes
\begin{equation}\label{heur2}
    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
\textcolor{blue}{
To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$. It turns out that such an estimate is quite delicate. We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
\end{rem}

Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate. Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).

\begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that for $x\in \Omega$,
\begin{align*}
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
\end{align*}
\end{thm}

@@

\begin{thm}\label{thm:wellposed1<p<2} Let $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. There exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that:
\begin{itemize}
    \item[(i)] If $1<p< 2$, then 
\begin{equation}\label{rate_p<2}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{ } \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{ } 
    \lim_{d(x)\to 0}\left( u^\varepsilon(x) \,d(x)^\alpha \right)= C_\alpha \varepsilon^{\alpha+1}
\end{equation}
where $\alpha = (p-1)^{-1}(2-p)$ and $C_\alpha = \alpha^{-1}(\alpha+1)^{\alpha+1}$.
%\begin{equation*}
%    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\alpha = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
%\end{equation*}
\item[(ii)] If $p=2$, then
\begin{equation}\label{rate_p=2}
    \lim_{d(x)\to 0} \left(-\frac{u^\varepsilon(x)}{\log(d(x))}\right) = \varepsilon.
\end{equation}
\end{itemize}
Furthermore, $u^\varepsilon$ is the maximal subsolution among all the subsolutions $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
\end{thm}
\noindent This is Theorem I.1 in \cite{Lasry1989} with an explicit dependence on $\varepsilon$. A proof of this theorem is carried out explicitly in Appendix for later use. Also, it is useful to note that $\alpha+1 = (p-1)^{-1}$. More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006}.

@@

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$. Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keeping track of all dependencies. We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
\end{rem}

\begin{lem} There exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
\end{equation*}
\end{lem}

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$. Here are some results in the literature: if $u$ solves ($f\in \mathrm{C}^1(\overline{\Omega}), f\geq 0$)
\begin{equation*}
\begin{cases}
    \lambda u + |Du|^p - f(x) - \Delta u = 0&\qquad\text{in}\;\Omega,\\
    u = +\infty&\qquad\text{on}\;\partial\Omega
\end{cases}
\end{equation*}
then we can have a better bound in a priori estimate (\cite{lions_quelques_1985}) 
\begin{equation*}
    |Du(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
\end{equation*}
where $\alpha = \frac{2-p}{p-1}$, while (\cite{alessio_asymptotic_2006}) gives an asymptotic behavior
\begin{equation*}
    \lim_{d(x)\to 0} \Big(Du(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0).
\end{equation*}
Here $\underline{x}$ is the unique projection of $x$ (near the boundary) onto $\partial\Omega$ and $\mathfrak{n}(x_0)$ is the unit outward normal vector of $\Omega$ at $x_0$. 
\paragraph{\textbf{Our version with $\varepsilon$}}
In our version, the problem with $\varepsilon$, we have 
\begin{equation*}
\begin{cases}
    \lambda u^\varepsilon + |Du^\varepsilon|^p - f(x) - \varepsilon\Delta u^\varepsilon = 0&\qquad\text{in}\;\Omega,\\
    u^\varepsilon = +\infty&\qquad\text{on}\;\partial\Omega
\end{cases}
\end{equation*}
we can obtain that
\begin{equation}\label{eq:yy}
    |Du^\varepsilon(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
\end{equation}
and 
\begin{equation}\label{eq:xx}
    \lim_{d(x)\to 0} \Big(Du^\varepsilon(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0)\varepsilon^{\alpha+1}.
\end{equation}

\paragraph{\textbf{The result that we need for Theorem \ref{main_thm2}}} The ideal estimate we are expecting is, there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
|Du^\varepsilon(x)| \leq C + \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}} \qquad\text{for}\;x\in \Omega.
\end{equation*}
This estimate can be proven following from a priori estimate $|Du^\varepsilon(x)|\leq C_\delta$ for $x\in \Omega_\delta$ and \eqref{eq:xx} if the limit in \eqref{eq:xx} is uniform in $\varepsilon$.

\paragraph{\textbf{Difficulty}} However, \eqref{eq:xx} is not uniform in $\varepsilon$ (at least from the method the authors Porretta and Veron use in \cite{alessio_asymptotic_2006}).
\end{rem}

%\begin{proof}[Proof of Theorem \ref{main_thm2}] Define

%\end{proof}

@@

\subsection*{Asymptotic behavior of derivatives}
We denote by $\nu(x)$ the outward unit normal vector at any point $x\in \partial{\Omega}$ and $\tau(x)$ the unitary tangent vector defined on $\partial{\Omega}$, i.e., $\nu(x)\cdot\tau(x) = 0$. We start by considering the case $p=2$.
\begin{equation*}
    \begin{cases}
    -\Delta u 
    \end{cases}
\end{equation*}

\subsection*{Existence and wellposedness of solution}
\begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] If $p\in (1,2)$, we use the ansatz $ u(x) = C_\varepsilon d(x)^{-\alpha}$ to find a solution for \eqref{eq:PDEeps}. Plug the ansatz into \eqref{eq:PDEeps} and compute 
\begin{equation*}
    |Du (x)|^p = \frac{(\alpha C_\varepsilon)^p }{d(x)^{p(\alpha+1)}}|D d(x)|^p \qquad\text{and}\qquad\varepsilon\Delta u(x) = \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{equation*}
Since $|D d(x)| = 1$ for $x$ near $\partial\Omega$, as $x\to \partial \Omega$, the explosive terms of the highest order are
\begin{equation*}
         C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}  -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)}.
\end{equation*}
Set the above to be zero to obtain that
\begin{equation}\label{e:relation}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
\end{equation}
For $0<\delta < \frac{1}{2}\delta_0$ and $\eta$ small, define
\begin{equation*}
\begin{split}
    \overline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha+\eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta, \qquad x\in \Omega_\delta,\\
    \underline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha-\eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta, \qquad x\in \Omega^\delta,
\end{split}
\end{equation*}
where $C_\alpha := \frac{1}{\alpha} (\alpha+1)^{\alpha+1} $, $M_\eta$ to be chosen. We will show that $\overline{w}_{\eta,\delta}$ is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$, while $\underline{w}_{\eta,\delta}$ is a subsolution of \eqref{eq:PDEeps} in $\Omega^\delta$. Compute
\begin{align*}
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{ (C_\alpha + \eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\alpha+\eta)^p \alpha^p\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
    & \qquad\qquad\qquad\qquad\qquad - \frac{(C_\alpha+\eta)\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{(C_\alpha+\eta)\alpha \varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+1}}\Delta d(x)\\
    &\geq M_\eta - f(x) + \underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p} - |Dd(x)|^2 + \frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right]}_{I}
\end{align*}
%\textcolor{orange}{(In the parenthesis of I, I think the first term should be $\nu^{p-1}|Dd(x)|^p$ instead of $\nu^{p-1}|Dd(x)|^{p-1}$.)}
where we use $(C_\alpha\alpha)^p = C_\alpha\alpha(\alpha+1)$ and $\nu = \frac{C_\alpha+\eta}{C_\alpha} \in (1,2)$ for small $\eta$. Let
\begin{equation*}
    \delta_\eta : = \frac{\alpha+1}{K_2}\left[\nu^{p-1}-1\right]
\end{equation*}
and $\delta_\eta \to 0$ as $\eta \to 0$.
Recall the definitions in \eqref{boundond}. To get  $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$, there are two cases to consider, depending on how large $d(x)-\delta$ is.
\begin{itemize}
    \item If $0< d(x)-\delta <\delta_\eta < \delta_0$ for $\eta$ small and fixed, then $|Dd(x)| = 1$, and thus $I\geq 0$. Hence $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$ if we choose $M_\eta \geq \max_{\overline{\Omega}} f$.
    %\textcolor{orange}{(Question: Here, $\eta$ is fixed right?)}
    \item If $d(x)-\delta\geq \delta_\eta$, then 
    \begin{equation*}
        I \leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2}\nu C_\alpha \alpha(\alpha+1)\left[\nu^{p-1}K_1^{p}+K_1^2+K_2K_0\right]\varepsilon^{\alpha+2}.
    \end{equation*}
    %\textcolor{orange}{(The first term in the bracket should be $\nu^{p-1}K_1^p$ instead of $\nu^{p-1}K_1^{p-1}$.)}

>>>>

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
\begin{equation}\label{heur1}
    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$. After taking derivative, heuristically, \eqref{heur1} becomes
\begin{equation}\label{heur2}
    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
We show in Lemma \ref{lem:boundDu^eps} that \eqref{heur2} gives the correct behavior of $Du^\varepsilon$ where $\alpha = \frac{2-p}{p-1}$. \\
\noindent
\textcolor{blue}{
To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$. It turns out that such an estimate is quite delicate. We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
\end{rem}

Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate for compactly supported $f$. Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).

\begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $1 < p\leq 2$ and $f$ is a compactly supported Lipschitz function defined on $\overline{\Omega}$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that for $x\in \Omega$,
\begin{align*}
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
\end{align*}
\end{thm}

@@

\begin{thm}\label{thm:wellposed1<p<2} Let $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. There exists a unique solution $u^\varepsilon\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that:
\begin{itemize}
    \item[(i)] If $1<p< 2$, then 
\begin{equation}\label{rate_p<2}
    %\frac{C_\varepsilon-\eta}{d(x)^\alpha}-\frac{M_\eta}{ } \leq u(x)\leq \frac{C_\varepsilon+\eta}{d(x)^\alpha}+\frac{M_\eta}{ } 
    \lim_{d(x)\to 0}\left( u^\varepsilon(x) \,d(x)^\alpha \right)= C_\alpha \varepsilon^{\alpha+1}
\end{equation}
where $\alpha = (p-1)^{-1}(2-p)$ and $C_\alpha = \alpha^{-1}(\alpha+1)^{\alpha+1}$.
%\begin{equation*}
%    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\alpha = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.
%\end{equation*}
\item[(ii)] If $p=2$, then
\begin{equation}\label{rate_p=2}
    \lim_{d(x)\to 0} \left(-\frac{u^\varepsilon(x)}{\log(d(x))}\right) = \varepsilon.
\end{equation}
\end{itemize}
Furthermore, $u^\varepsilon$ is the maximal subsolution among all the subsolutions $v\in W^{2,r}(\Omega)$ (for all $r>0$) of \eqref{eq:PDEeps}.
\end{thm}
\noindent This is Theorem I.1 in \cite{Lasry1989} with an explicit dependence on $\varepsilon$. A proof of this theorem is carried out explicitly in Appendix for later use. Also, it is useful to note that $\alpha+1 = (p-1)^{-1}$. More results on the behavior of the gradient of $u^\varepsilon$ can be found in \cite{alessio_asymptotic_2006} and Lemma \ref{lem:boundDu^eps}, where we show $|Du^\varepsilon|\leq C + C\left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$.

@@

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$. Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keep track of all dependencies. We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
\end{rem}

\begin{lem}\label{lem:boundDu^eps} For all $\varepsilon$ small enough, there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation}\label{eq:es_final}
|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
\end{equation}
\end{lem}

\begin{proof}[Proof of Lemma \ref{lem:boundDu^eps}] %Let us consider $0<\varepsilon < \min\{4\delta_0,1\}$. 
Let us fix $x_0 \in \Omega\backslash \Omega_{\delta_0}$ and let $\delta = \frac{1}{4}d(x_0)$. Let 
\begin{equation*}
    v(x) = \frac{1}{\delta}u^\varepsilon(x_0+\delta x), \qquad x\in B(0,2).   
\end{equation*}
We have $Dv(x) = Du^\varepsilon(x_0+\delta x)$ and $\Delta v(x) = \delta \Delta u^\varepsilon(x_0+\delta x)$ for $x\in B(0,2)$. The equation for $v$ is given by
\begin{equation*}
    \delta v(x) + |Dv(x)|^p - \tilde{f}(x) - \frac{\varepsilon}{\delta}\Delta v(x) = 0 \qquad\text{in}\;B(0,2),
\end{equation*}
where $\tilde{f}(x) = f(x_0+\delta x)$ defined on $\overline{B(0,2)}$. We note that $\Vert \tilde{f}\Vert_{L^\infty}\leq \Vert f\Vert_{L^\infty}$ and 
\begin{equation*}
    B(x_0,2\delta)\subset \Omega_{2\delta}\subset\subset\Omega.
\end{equation*}
By Lemma \ref{lem:super_refined}, there is a constant $C$ independent of $\delta,\varepsilon$ such that 
\begin{equation*}
     \delta\Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)} \leq \Vert u^\varepsilon\Vert_{L^\infty(\Omega_{2\delta}))} \leq C\left(1 + \frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right).
\end{equation*}
Note that $p = \frac{\alpha+2}{\alpha+1}$ and $\alpha+1 = \frac{1}{p-1}$, we apply Theorem 3.1 in \cite{Armstrong2015} to obtain 
\begin{equation*}
\begin{split}
    \sup_{x\in B(0,1)}|Dv(x)| &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\frac{1}{p-1}} + \left(\Vert f\Vert_{L^\infty}+\delta \Vert v\Vert_{L^\infty\left(B\left(0,\frac{3}{2}\right)\right)}\right)^{\frac{1}{p}}\right] \\
    &\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)^{\frac{\alpha+1}{\alpha+2}}\right]\leq C \left(1+\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1}\right).
    %&\leq C\left[\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} + \left(1+\left(\frac{\alpha+1}{\alpha+2}\right)\frac{\varepsilon^{\alpha+1}}{\delta^\alpha}\right)\right] \leq C\left[1+2\left(\frac{\varepsilon}{\delta}\right)^{\alpha+1} \right]
\end{split}
\end{equation*}
%where we use Bernoulli's inequality and the fact that $\delta \leq 1$. 
Replace $\delta = \frac{1}{4}d(x_0)$ we obtain
\begin{equation*}
    |Du^\varepsilon(x_0)| = |Dv(0)| \leq C\left(1+ \left(\frac{\varepsilon}{d(x_0)}\right)^{\alpha+1}\right).
\end{equation*}
In other words, we obtain \eqref{eq:es_final} for all $x\in \Omega\backslash\Omega_{\delta_0}$. From Theorem \ref{thm:grad_1} there exists a constant $C$ independent of $\varepsilon$ such that $|Du^\varepsilon(x)|\leq C$ for all $x\in \Omega_{\delta_0}$ and thus the proof is complete.
\end{proof}

\begin{rem} As a consequence, the constant $C_{\frac{\kappa}{2}}$ in Theorem \ref{thm:rate_doubling2} satisfies
\begin{equation*}
    C_{\frac{\kappa}{2}} \leq C\left(1+\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1}\right)
\end{equation*}
where $C$ is a constant independent of $\varepsilon$ and $\kappa$.
\end{rem}

\begin{proof}[Proof of Theorem \ref{main_thm2}] Let $L$ be the Lipschitz constant of $f$. For $0 < \kappa <\delta_0$ we define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
\begin{equation*}
    0\leq f - f_\kappa \leq L\kappa.
\end{equation*}
Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} and $u_k$ be the solution to \eqref{eq:PDE0} with $f$ being replaced by $f_k$, respectively. By the same argument as in the proof of Theorem \ref{main_thm1}, we have
\begin{equation*}
  0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega
\end{equation*}
and
\begin{equation*}
    0\leq u(x) - u_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega.
\end{equation*}
By Theorem \ref{thm:rate_doubling2} and Lemma \ref{lem:boundDu^eps} we have 
\begin{equation*}
\begin{aligned}
    u_\kappa^\varepsilon(x) - u_\kappa(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} \left(1+ \left(\frac{\varepsilon}{\kappa}\right) +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon,  &\quad p <2, \\
    u_\kappa^\varepsilon(x) - u_\kappa(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C\left(\frac{\varepsilon}{\kappa}\right) \left(1+\frac{\varepsilon}{\kappa}\right)+ nc \varepsilon, &\quad p=2.
\end{aligned}
\end{equation*}
Therefore
\begin{equation*}
    u^\varepsilon(x)-u(x)\leq 2L\kappa + \Big(u^\varepsilon_\kappa(x) - u_\kappa(x)\Big) \leq 2L\kappa+C_{\kappa}\varepsilon
\end{equation*}
where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported.

@@

\subsection*{Existence and wellposedness of solution}
\begin{proof} [Proof of Theorem \ref{thm:wellposed1<p<2}] If $p\in (1,2)$, we use the ansatz $ u(x) = C_\varepsilon d(x)^{-\alpha}$ to find a solution for \eqref{eq:PDEeps}. Plug the ansatz into \eqref{eq:PDEeps} and compute 
\begin{equation*}
\begin{split}
    |Du (x)|^p &= \frac{(\alpha C_\varepsilon)^p }{d(x)^{p(\alpha+1)}}|D d(x)|^p,\\
    \varepsilon\Delta u(x) &= \frac{\varepsilon C_\varepsilon\alpha(\alpha+1)}{d(x)^{\alpha+2}}|D d(x)|^2 - \frac{\varepsilon C_\varepsilon\alpha}{d(x)^{\alpha+1}}\Delta d(x).
\end{split}
\end{equation*}
Since $|D d(x)| = 1$ for $x$ near $\partial\Omega$, as $x\to \partial \Omega$, the explosive terms of the highest order are
\begin{equation*}
         C_\varepsilon^p \alpha^p d^{-(\alpha+1)p}  -\varepsilon C_\varepsilon \alpha(\alpha+1)d^{-(\alpha+2)}.
\end{equation*}
Set the above to be zero to obtain that
\begin{equation}\label{e:relation}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_\varepsilon = \left(\frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}\right) \varepsilon^{\frac{1}{p-1}} = \frac{1}{\alpha}(\alpha+1)^{\alpha+1}\varepsilon^{\alpha+1}.
\end{equation}
For $0<\delta < \frac{1}{2}\delta_0$ and $\eta$ small, define
\begin{equation*}
\begin{split}
    \overline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha+\eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta, \qquad x\in \Omega_\delta,\\
    \underline{w}_{\eta,\delta}(x) &:= \frac{(C_\alpha-\eta)\varepsilon^{\alpha+1}}{(d(x)+\delta)^\alpha} - M_\eta, \qquad x\in \Omega^\delta,
\end{split}
\end{equation*}
where $C_\alpha := \frac{1}{\alpha} (\alpha+1)^{\alpha+1} $, $M_\eta$ to be chosen. We will show that $\overline{w}_{\eta,\delta}$ is a supersolution of \eqref{eq:PDEeps} in $\Omega_\delta$, while $\underline{w}_{\eta,\delta}$ is a subsolution of \eqref{eq:PDEeps} in $\Omega^\delta$. Compute
\begin{align*}
    \mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right](x) &= \frac{ (C_\alpha + \eta)\varepsilon^{\alpha+1}}{(d(x)-\delta)^\alpha} + M_\eta + \frac{(C_\alpha+\eta)^p \alpha^p\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^p - f(x) \\
    & \qquad\qquad\qquad\qquad\qquad - \frac{(C_\alpha+\eta)\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}|D d(x)|^2 + \frac{(C_\alpha+\eta)\alpha \varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+1}}\Delta d(x)\\
    &\geq M_\eta - f(x) + \underbrace{\frac{\nu C_\alpha\alpha(\alpha+1)\varepsilon^{\alpha+2}}{(d(x)-\delta)^{\alpha+2}}\left[\nu^{p-1}|Dd(x)|^{p} - |Dd(x)|^2 + \frac{(d(x)-\delta)\Delta d(x)}{\alpha+1}\right]}_{I}
\end{align*}
%\textcolor{orange}{(In the parenthesis of I, I think the first term should be $\nu^{p-1}|Dd(x)|^p$ instead of $\nu^{p-1}|Dd(x)|^{p-1}$.)}
where we use $(C_\alpha\alpha)^p = C_\alpha\alpha(\alpha+1)$ and $\nu = \frac{C_\alpha+\eta}{C_\alpha} \in (1,2)$ for small $\eta$. Let
\begin{equation*}
    \delta_\eta : = \frac{\alpha+1}{K_2}\left[\nu^{p-1}-1\right]
\end{equation*}
and $\delta_\eta \to 0$ as $\eta \to 0$.
Recall the definitions in \eqref{boundond}. To get  $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$, there are two cases to consider, depending on how large $d(x)-\delta$ is.
\begin{itemize}
    \item If $0< d(x)-\delta <\delta_\eta < \delta_0$ for $\eta$ small and fixed, then $|Dd(x)| = 1$, and thus $I\geq 0$. Hence $\mathcal{L}^\varepsilon\left[\overline{w}_{\eta,\delta}\right]\geq 0$ if we choose $M_\eta \geq \max_{\overline{\Omega}} f$.
    %\textcolor{orange}{(Question: Here, $\eta$ is fixed right?)}
    \item If $d(x)-\delta\geq \delta_\eta$, then 
    \begin{equation*}
        I \leq \left(\frac{1}{\delta_\eta}\right)^{\alpha+2}\nu C_\alpha \alpha(\alpha+1)\left[\nu^{p-1}K_1^{p}+K_1^2+K_2K_0\right]\varepsilon^{\alpha+2}.
    \end{equation*}
    %\textcolor{orange}{(The first term in the bracket should be $\nu^{p-1}K_1^p$ instead of $\nu^{p-1}K_1^{p-1}$.)}
